Simulated Observations of Young Gravitationally Unstable Protoplanetary Discs

### 2013-05-03 young_pp_discs.tex
small changes

{\bf Whilst photochemistry was not included in I2011, it is unclear to what extent the radiation from the protostar will impact upon the disc, given that material infalling from the envelope and newly forming outflows will be obscuring the star. Column densities between upper layers of the disc and the protostar in the model used here are on the order of 10$^{23}$ cm$^{-2}$ (is this enough to block the protostars visible and UV?). This is in contrast to later stages of disc evolution where the envelope has been almost entirely cleared (e.g. Walsh et. al), in this case it is clear that the chemistry in the upper layers of the disc will be dominated by photo-chemical processes.}

@@

{\bf The disc model used does not include magnetic fields, including magnetic fields may suppress GI and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction (Joos et al. 2012, Li et al. 2013). This would mean that if observations similar to the ones we have described are made constraints could be placed on B-field strength within cores/discs. \smallskip Futher work to improve these simulated observations would include looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}

>>>>

{\bf Whilst photochemistry was not included in I2011, it is unclear to what extent the radiation from the protostar will impact upon the disc, given that material infalling from the envelope and newly forming outflows will be obscuring the star. Column densities between upper layers of the disc and the protostar in the model used here are on the order of 10$^{23}$ cm$^{-2}$ (is this enough to block the protostars visible and UV?). This is in contrast to later stages of disc evolution where the envelope has been almost entirely cleared (e.g. Walsh et. al 2012), in this case it is clear that the chemistry in the upper layers of the disc will be dominated by photo-chemical processes.}

@@

{\bf The disc model used does not include magnetic fields, including magnetic fields may suppress GI and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction (Joos et al. 2012, Li et al. 2013). This would mean that if observations similar to the ones we have described are made constraints could be placed on B-field strength within cores/discs. \smallskip }
{\bf Futher work to improve these simulated observations would include looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
